Molecular dynamics simulation of synchronization in driven particles

### 2021-02-09 manuscript/manuscript_ajp_2020.tex
editing introduction

\begin{abstract}
  Synchronization
  plays a key role in many physical processes.
  We discuss a simple
  numerical model %that
  of synchronized particles 
  %exhibits
  %provides insight
  %to synchronization behavior
  %and
  %atoms on surfaces.
  %voltage driven superconducting vortices
  %confined in a Josephson junction,
  %and ac and dc driven
  %charge and spin density waves.
  %We present the basics
  using
  molecular dynamics simulations
  for particles moving through
  a viscous liquid.
  %Simplified models
  %such as 
  %What problem did you study and why is it important?
  Modeling synchronization
  with simulations and table-top experiments
  can 
  provide insight
  to complex behaviors
  in the natural world.
  We drive 
  particles
  across a washboard potential energy landscape, 
  a 
  common 
  technique to isolate complex 
  synchronized patterns 
  in both simulations and experiments.
  %as observed in 
  %experiments %al systems 
  %of %interest to condensed matter physics %including 
  %magnetically driven colloidal particles
  %confined by light-fields.
  %exhibit a variety of synchronization effects.
  %in
  %  Numerical model
  %
  %applied to single and multiple particle systems.
  %so we model the dynamics of each particle
  %with 
  %overdamped equations of motion.
  Our results show a variety of synchronization effects 
  in single and multi-particle systems, 
  %and detect synchronization using
  %measurements of
  which we characterize with
  plots of 
  particle velocity as a function of applied driving force,
  and phase diagrams of position versus velocity.
  %We demonstrate how to 
  %visualize
  %the system with
  %numerical representations of the landscape
  %and
  %animations of the particle motion.
  %We include sample code
  %and exercises for students
  %with 
  %opportunities
  %to reproduce our results and propose
  %new numerical experiments.
  %With only a few particles in two-dimensions,
  %the simulation runs quickly,
  %making this an appropriate model for undergraduates to explore.  
\end{abstract}
% AJP requires an abstract for all regular article submissions.
% Abstracts are optional for submissions to the "Notes and Discussions" section.

@@

\section{Introduction} %
%
%Outline
%------------------------------------------------------------------
%synchronization = widest audience possible
Synchronization is a universal phenomena
in which individual oscillators adjust frequency due
to external stimulus \cite{Pikovsky2003}.
Many everyday systems
exhibit in-phase coupled oscillations %of components 
such as the
flickering patterns of
candle flames mediated by temperature fluctuations \cite{Okamoto2016},
vibrations of singing wineglasses interacting 
through sound waves \cite{Arane2009}, 
and metronomes vibrating through a supporting platform \cite{Jia2015}.
Biological systems benefit from cooperative
synchronization -- %such as 
birds coordinate wing flaps
to optimize energy use during flight \cite{Portugal2014},
frogs alternate croaking patterns \cite{Aihara2014},
humans clap in time with music \cite{Tranchant2016}
and 
at a cellular level, 
neurons simultaneously fire in cardiac muscle \cite{MartinHall1999}
and brain tissue \cite{Singer1999}.
External forcing can cause or regulate 
synchronization. % is often achieved via external forcing
%such as when
%single particle oscillators
For instance,
an electrical pacemaker %(an electrical generator)
pulses to regulate a heart beat,
and 
a flashing light can modify the
pattern of flashing fireflies .% \cite{Agrawal2013}.

%Christiaan Huygens 
%[has been adapted into many useful technologies...]
A particular form of 
synchronization is phase-locking or mode-locking,
which first appeared in the scientific literature
with 
Huygens' 1665 experiments on
the 
motions of two wall-mounted pendulum clocks.
Huygens demonstrated the tendency of
the pendula 
to swing in time, 
even when started out of phase,
due to interactions through the wall \cite{Bennett2002}.
%phase locking
Dynamical systems %with multiple frequencies
exhibit phase-locking 
when oscillators with different rhythms adjust %couple
to a frequency ratio or mode 
of an integer number \cite{Bak1986}.
%Dynamical mode locking
%The phenomena
Synchronization 
is often studied with simple computational models
and can be visualized 
with phase
plots or Lissajous figures.
In phase space 
a mode-locked system is confined to 
a closed loop in a 
parametric space showing the relationship between two periodic functions
with patterns determined by the mode, % frequency ratio,
first reported in 1857 \cite{Lissajous1857}
and easily generated with a computer code 
or oscilloscope \cite{Tong1997}. 
%with a frequency generator,
%where two combined frequencies at perpendicular orientations
%({\it As we will demonstrate in phase plots in Figs. X, Y, Z})
It should be noted that the term phase
has two scientific meanings, 
``oscillation phase'' and ``phase space''
%refer to different uses of the word ``phase.''
Oscillation phase $\phi_0$ is the constant portion of the argument in a periodic function
  $\sin{(\omega t + \phi_0)}$ while phase space refers
  to plots of velocity versus position (such as $v_y$ vs. $y$)
  that are used to characterize oscillating systems.

@@

Complex dynamics can be studied with
colloid particles with experiments and simulation.
In typical experiments colloids are spheres of 
plastic suspended in
highly de-ionized water or silica in suspended in organic solvent.
%experimental - colloids specifically
Because 
the spheres are a few microns in size
and move at rates of microns per second,
the position of a particle %is large and slow enough to
can be imaged as a function of time 
with a traditional optical camera.
%due to the large size and slow speed of the particles.
Individual colloids exhibit 
Brownian motion,
where particles change direction %in a seemingly random fashion
due to 
collisions 
with unseen particles comprising the suspending fluid \cite{}.
%[elaborate - move to associated problems?].

Light is a
tool for manipulating the colloidal environment.
A single laser beam can be used to create an optical trap,
which uses 
photon radiation pressure to
control colloid motions \cite{Ashkin1997}.
A circular optical trap is designed
with a local energy minimum 
at its center.
A colloid in the beam center is subject to a
uniform distribution of photon bombardment,
and motions away from the center create a net force
due to an uneven 
distribution of photon collisions on its surface.
%Colloids at a trap edge
%experience a net force
%due to the 
Depending on the %shape of the trap and
location of the particle in the trap,
the radiation pressure either restores colloids toward the local minima
or ejects it from the trap.
An optically trapped colloid executing Brownian motion
is a useful probe of microscopic forces,
and has been studied in detail in Ref.~\cite{Volpe2013}.

%In experiments  
 Complex environments can be
 engineered with light by %, typically made 
 using diffraction gratings to create a patterned
 potential energy landscape 
 with one or more laser beams \cite{Grier2003}.
 How a particle moves
 in an optical landscape can
 change
 when 
 subject to external driving forces.
 Individual particles can
 perform 
 synchronized % with the environment
 motions
 that lock together particle location and velocity.
 Experimental studies of
 the microscopic dynamics 
 colloids performing phase-locked motions
 produce step-by-step diagrams
 of particle dynamics useful for
 understanding synchronization at a single particle level \cite{Juniper2015}.

@@

  {\bf With no applied driving force,
    find 
  the minimum temperature required for a single particle
  to hop over maxima in the potential landscape.}
  %$T_{min} > A_p$.
  Assume the particle is confined to
  move along the $y-$direction,
  include Brownian motion 
  in the model.
  In Fig.~\ref{fig:brownian},
  we demonstrate the transition
  from pinned to hopping
  in 
  %Measure the position vs. time
  a non-driven colloid for $T/A_p = 4.0, 5.0, 6.0$.
  The crossover
  to a hopping regime occurs at $T/A_p \approx 5.6$.
  %Reproduce these results.  
  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{brownian_particle_dt0.1}.pdf}
      \caption{
        Motion of a particle undergoing Brownian motion
        on a washboard potential
        energy landscape.
        (a) $T/A_p = 4.0$ no hopping occurs.
        (b) $T/A_p = 5.0$ a single hop occurs at $t = 130000$
        across a distance of $\Delta y = 2 \lambda$.
        (c) $T/A_p = 6.0$ many hops occur.
        Note the scale of the $y-$axis differs in each panel
        and the time scale is
        much greater than in Fig.~\ref{fig:1}.
      }
      \label{fig:brownian}
    \end{figure}
  \end{center}
  In Fig.~\ref{fig:brownian}
  we show the position versus time of a particle
  confined to a sinusoidal landscape
  undergoing Brownian motion.
  We increase the temperature relative
  to the amplitude of the landscape
  troughs until the particle enters a hopping regime.
  In  Fig.~\ref{fig:brownian}(a)
  the temperature is $T/A_p = 4.0$.
  The particle executes a 
  random walk centered at the potential minima $y/\lambda = 10$.
  We ran many simulations and never observed a hop to another minima
  within this simulation time.  
  In  Fig.~\ref{fig:brownian}(b)
  $T/A_p = 5.0$ where hops between
  potential minima are possible but not probable,
  a single hop occurs from
  $y/\lambda = 10$ to $y/\lambda = 12$ at
  $t \sim 40000 \tau$ and 
  $y/\lambda = 10$ to $y/\lambda = 8$ at
  $t \sim 280000 \tau$.
  In other simulations with identical parameters,
  we sometimes observed no hops or two hops between minima,
  as expected with random fluctuating systems.
  In  Fig.~\ref{fig:brownian}(c)
  $T/A_p = 6.0$ 
  we observe many hops.
  The random thermalized kicks are
  sufficiently large to make the particle perform
  what appears to be 
  a random walk of hops atop the substrate.
  %in addition to the small scale random walk executed
  %by all particles in this section.

@@

  In Fig.~\ref{fig:hops}
  we show the effects of lowering the frequency
  of applied driving force,
  holding the remaining parameters fixed 
  to 
  $F^{dc}=0.1$, $F^{ac}=0.05$, and $A_p = 0.1$.
  We observe no backward steps 
  ($n_b = 0$) 
  across a broad range of frequencies.
  The number of forward steps 
  $n_f$ increases as frequency decreases.
  Low frequencies
  result in sustained positive or negative motion of a particle,
  where in Fig.~\ref{fig:hops}(e)
  the particle reaches the top edge of the system
  and wraps back to $y=0$.
  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{parameters_fig5}.pdf}
      \caption{
        Motion of a particle with the same values of $F^{dc} = 0.1$ and $F^{ac} = 0.05$ as Fig.~\ref{fig:1} and decreasing frequency as marked.
        In (e) the particle wraps the periodic boundary conditions.
      }
      \label{fig:hops}
    \end{figure}
  \end{center}
  %In Fig.~\ref{fig:hops}

  In Fig.~\ref{fig:hops_back}
  we fix $f=0.01$, $F^{dc}=0.1$, and and $A_p = 0.1$.
  We show the results for increasing $F^{ac} = 0.2, 0.3, 0.4$.
  %of the system for our original parameters.
  Here $n_b$ increases from $n_b = 0$ in (a) to
  $n_b = 2$ in (b) to $n_b = 4$ in (c).  
  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{parameters_fig6}.pdf}
      \caption{
        Motion of a particle with the same values of $F^{dc}$ and frequency as Fig.~\ref{fig:1} and increasing $F^{ac}$.
        (a) The particle moves forward six minima with no steps backward.
        (b) The particle moves forward eight minima with two steps backward.
        (c) The particle moves forward nine minima with four steps backward.
      }
      \label{fig:hops_back}
    \end{figure}
  \end{center}
  %In Fig.~\ref{fig:hops}

  Shapiro steps
%\item Frenkel-Kontorova and competing length scales for low temperature systems where thermal fluctuations are negligible
%  \item The Fokker-Planck Equation
%  \item Aubrey-Kontorova + commensurability
%  \item nanotribology
 %   kink motion
 %   Vanossi et al J.Phys.: Condens. Matter 19 (2007)
  %\item

@@

\section{Conclusion}
\label{sec:conclusion}	% You can label sections for reference
A single particle oscillator
in a potential well is 
like a skateboarder in a half-pipe or
a child on a swing.
%If subject to an applied force,
A confined oscillator may 
synchronize its location
to the periodic pattern of the external drive,
moving back and forth in time with
the beat. 
The relationship between the driving force and
landscape can change the pattern of motion.  
With a constant or 
dc drive the landscape modulates 
the particle velocity, below some threshold  
the dc force is not strong enough to push the particle
across a potential maximum so the average velocity is zero,
a phenomena referred to as pinning \cite{Reichhardt2017}.
Above the pinning threshold,
a particle subject to a constant
drive force will increase its speed at a rate propotional
to the external drive.  
%and dissipating energy from the system at all driving forces.
A sinusoidal or ac drive can create mode-locking,
where the average particle velocity
is fixed for a range of dc drive forces \cite{Reichhardt2015}.
This synchronization phenomena
is useful for understanding the complex dynamical 
systems.

%Fundamental models
%of synchronization 
%can %include many coupled oscillators
%or
%focus on
We have used 
a single particle driven across a periodic potential landscape 
%Single particle studies are useful
to study synchronization dynamics
that arise due to the interplay
between environmental and external forces.
%due to interactions between particles.
Our simulations reproduce results presented in 
Juniper {\it et al.} \cite{Juniper2015} %, Juniper2018}
which demonstrate 
mode locking in
experiments and simulations of 
driven colloids on a
periodic optical landscape.
Due to the relative ease of
manipulation and imagining, 
colloids are used as experimental models
for systems %relatively
hard to access and visualize 
such as cold atoms or electron gases \cite{Grier2003}.
%Collections of colloids can
%be used to study the properties of solids and liquids
%or more exotic systems 
%Oscillators ordered into chains or lattices.
%has many important
%technological applications
Dynamical mode-locking, the primary synchronization
effect explored in this paper, 
is %often
observed
in quantum electronic
devices such as Josephson junctions \cite{Josephson1962,Josephson1965}.
%A single junction contains 
%two superconductoring layers which sandwich an insulating layer.
%When subject to an external voltage,
%Cooper pairs in the superconducting materials
%tunnel through the insulating layer.
Phase-locking is observed as 
stepped regions in current-voltage (I-V) relationship in these devices,
where voltage is the analog of external driving force
and current is that of particle velocity.
Known as Shapiro steps, % \cite{},
these phase locked currents  
have been observed due to applied ac voltages in 
single Josephson junctions \cite{Shapiro1963, Golubov2004} and
coupled arrays of junctions \cite{Benz1990}.
Shapiro steps vary in width depending on the strength of the
applied ac forces,
and are observed in a variety of systems
displaying
%are hallmarks of
non-Ohmic behavior in voltage-current curves,
including
ac and dc driven
charge and spin density waves
and superconducting vortices in landscapes 
engineered with periodic patterns of pinning sites.
Thus the study of
mode-locking is a useful probe 
of complex quantum mechanical systems.
Our results can be relevant 
to synchronization effects
in a broad range of experiments systems
including optically confined colloids,
superconductors with periodic pinning arrays, 
and the charge and spin of atomic systems.

@@

@@

      quote: Phase engineering techniques are used to control the dynamics of long-bosonic Josephson-junction arrays built by linearly coupling Bose-Einstein condensates.
    \bibitem{Zhang2020} Dengling Zhang, Haibo Qiu, and Antonio Muñoz Mateo, Unlocked-relative-phase states in arrays of Bose-Einstein condensates, Phys. Rev. A {\bf 101}, 063623 (2020).

>>>>

\begin{abstract}
  Synchronization
  plays a key role in many physical processes.
  We discuss a simple
  numerical model %that
  of synchronized particles 
  %exhibits
  %provides insight
  %to synchronization behavior
  %and
  %atoms on surfaces.
  %voltage driven superconducting vortices
  %confined in a Josephson junction,
  %and ac and dc driven
  %charge and spin density waves.
  %We present the basics
  using
  molecular dynamics simulations
  for particles moving through
  a viscous liquid.
  %Simplified models
  %such as 
  %What problem did you study and why is it important?
  Modeling synchronization
  with simulations and table-top experiments
  can 
  provide insight
  to complex behaviors
  in the natural world.
  We drive 
  particles
  across a washboard potential energy landscape, 
  a 
  common 
  technique to isolate complex 
  synchronized patterns 
  in both simulations and experiments.
  %as observed in 
  %experiments %al systems 
  %of %interest to condensed matter physics %including 
  %magnetically driven colloidal particles
  %confined by light-fields.
  %exhibit a variety of synchronization effects.
  %in
  %  Numerical model
  %
  %applied to single and multiple particle systems.
  %so we model the dynamics of each particle
  %with 
  %overdamped equations of motion.
  Our results show a variety of synchronization effects 
  in single particle systems, 
  %and detect synchronization using
  %measurements of
  which we characterize by 
  plotting 
  particle velocity as a function of applied driving force 
  and phase diagrams of position versus velocity.
  %We demonstrate how to 
  %visualize
  %the system with
  %numerical representations of the landscape
  %and
  %animations of the particle motion.
  %We include sample code
  %and exercises for students
  %with 
  %opportunities
  %to reproduce our results and propose
  %new numerical experiments.
  %With only a few particles in two-dimensions,
  %the simulation runs quickly,
  %making this an appropriate model for undergraduates to explore.  
\end{abstract}
% AJP requires an abstract for all regular article submissions.
% Abstracts are optional for submissions to the "Notes and Discussions" section.

@@

\section{Introduction} %
%
%Outline
%------------------------------------------------------------------
%synchronization = widest audience possible
Synchronization is a universal phenomena
in which
individual oscillators change frequency due
to external stimuli \cite{Pikovsky2003}.
The
flickering patterns of
candle flames mediated by temperature fluctuations \cite{Okamoto2016},
vibrations of singing wineglasses interacting 
through sound waves \cite{Arane2009}, 
and metronomes vibrating through a supporting platform \cite{Jia2015}
are examples of in-phase coupled oscillations. %of components 
Biological systems benefit from cooperative
synchronization -- %such as 
birds coordinate wing flaps
to optimize energy use during flight \cite{Portugal2014},
frogs alternate croaking patterns \cite{Aihara2014},
humans clap in time with music \cite{Tranchant2016}
and 
at a cellular level, 
neurons simultaneously fire in cardiac muscle \cite{MartinHall1999}
and brain tissue \cite{Singer1999}.
External forcing can cause or regulate 
synchronization %. % is often achieved via external forcing
%such as when
%single particle oscillators
-- %For instance,
an electrical pacemaker %(an electrical generator)
regulates a heart beat 
and 
a pulsed light modifies the
flashing pattern of fireflies .% \cite{Agrawal2013}.

%Christiaan Huygens 
%[has been adapted into many useful technologies...]
Synchronized phase-locking or mode-locking 
first appeared in the scientific literature
with 
Huygens' 1665 experiments on
motions of 
pendula in two wall-mounted clocks.
Even when started out of phase, 
%Huygens demonstrated the tendency of
coupled pendula tend to swing in time
due to interactions through the wall \cite{Bennett2002}.
%phase locking
A locked-mode is an integer frequency ratio.
In Huygens clocks, 
the pendula were observed swing at same rate in a 1:1 mode.
For simple pendula of different lengths,
a 2:1 mode can be seen when a pendulum four
times the length of the other swings with twice the period.
%
%to a mode or frequency ratio  
%of an integer number \cite{Bak1986}.
%Dynamical mode locking
%The phenomena
Synchronization 
%is often studied with simple computational models and
can be visualized 
with phase
plots or Lissajous figures, 
first reported in 1857 \cite{Lissajous1857}.
%and easily generated with a computer code 
%or oscilloscope \cite{Tong1997}. 
A mode-locked system is confined to 
a closed loop in  
parametric phase space % showing the relationship between two periodic functions
with patterns determined by the mode. % frequency ratio,
({\it As we will demonstrate in phase plots in Figs. X, Y, Z}).
%with a frequency generator,
%where two combined frequencies at perpendicular orientations
Note the term phase
has two scientific meanings:  
%``oscillation phase'' and ``phase space.''
%refer to different uses of the word ``phase.''
oscillation phase $\phi_0$ is the constant of the argument
in a periodic function
$\sin{(\omega t + \phi_0)}$ and phase space is
used to characterize oscillating systems with
parametric plots of $v_y$ vs. $y$.

@@

Complex dynamics can be studied with
colloid particles in experiments or simulations.
Typical colloids are   
plastic spheres suspended in
de-ionized water or silica beads suspended in organic solvent.
%experimental - colloids specifically
Because 
colloids are large %-- a few microns in size
and move slowly %-- a few microns per second,
particle position 
can be imaged in real time 
with an optical camera \cite{Pertsinidis2001}. %(see Table ~\ref{tab:1}).
Experimental measurements of 
step-by-step dynamics of 
colloids performing phase-locked motions
are useful for
understanding synchronization at a single particle level \cite{Juniper2015}.

%due to the large size and slow speed of the particles.
%Individual colloids exhibit 
%Brownian motion,
%where particles change direction %in a seemingly random fashion
%due to 
%collisions 
%with unseen particles comprising the suspending fluid \cite{}.
%[elaborate - move to associated problems?].

Light is a
tool for manipulating the colloidal environment.
A circular optical trap uses 
radiation pressure from 
a laser beam to confine colloids \cite{Ashkin1997}.
%Since photon density is high at the beam center,
A colloid centered in the beam is %subject to a
uniformly bombarded by photons while 
%form a circular pattern with a higher density 
%central 
%energy minimum.
%optical trap  trap colloids
%with radiation pressure  which uses  photon 
%control colloid motions 
%A  is designed
off-center colloids %away from center
collide with photons unevenly,
creating a net force.
%Colloids at a trap edge
%experience a net force
%due to the 
Depending on the %shape of the trap and
location of the particle in the trap,
the radiation pressure either moves colloids toward the local minimum 
or ejects it from the trap.
An optically trapped colloid executing Brownian motion
is a useful probe of microscopic forces,
and has been studied in detail in Ref.~\cite{Volpe2013}.
%In experiments
Diffraction gratings can be used to create
more complex light environments, 
%with one or more laser beams,
such as periodic patterns of minima
suitable for synchronization studies \cite{Grier2003}.

A single particle oscillator
in a potential well is 
like a skateboarder in a half-pipe or
a child on a swing.
%If subject to an applied force,
 How a particle moves
 in an optical landscape can
 change
 when 
 subject to external driving forces.
 %Individual particles can
 %move with synchronized location and velocity
 % with the environment
 %motions
 %that lock together particle .
 A confined oscillator may 
 synchronize its location
 to the periodic pattern of the external drive,
 moving back and forth in time with
 the beat. 
 %The relationship between the driving force and
 %landscape can change the pattern of motion.  
 With a constant or 
 dc drive the landscape modulates 
 the particle velocity, below some threshold  
 the dc force is not strong enough to push the particle
 across a potential maximum so the average velocity is zero,
 a phenomena referred to as pinning \cite{Reichhardt2017}.
 Above the pinning threshold,
 a particle subject to a constant
 drive force will increase its speed at a rate propotional
 to the external drive.  
 %and dissipating energy from the system at all driving forces.
 A sinusoidal or ac drive can create mode-locking,
 where the average particle velocity
 is fixed for a range of dc drive forces \cite{Reichhardt2015}.
 %This synchronization phenomena
 %is useful for understanding the complex dynamical 
 %systems.

@@

  {\bf With no applied driving force,
    find 
  the minimum temperature required for a single particle
  to hop over maxima in the potential landscape.}
  %$T_{min} > A_p$.
  Assume the particle is confined to
  move along the $y-$direction,
  include Brownian motion 
  in the model.
  In Fig.~\ref{fig:brownian},
  we demonstrate the transition
  from pinned to hopping
  in 
  %Measure the position vs. time
  a non-driven colloid for $T/A_p = 4.0, 5.0, 6.0$.
  The crossover
  to a hopping regime occurs at $T/A_p \approx 5.6$.
  %Reproduce these results.  
  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{brownian_particle_dt0.1}.pdf}
      \caption{
        Motion of a particle undergoing Brownian motion
        on a washboard potential
        energy landscape.
        (a) $T/A_p = 4.0$ no hopping occurs.
        (b) $T/A_p = 5.0$ a three hops occur %at $t = 130000$
        across distances of $\Delta y = 2 \lambda$.
        (c) $T/A_p = 6.0$ many hops occur.
        Note the scale of the $y-$axis differs in each panel
        and the time scale is
        much greater than in Fig.~\ref{fig:0}.
      }
      \label{fig:brownian}
    \end{figure}
  \end{center}
  In Fig.~\ref{fig:brownian}
  we show the position versus time of a particle
  confined to a sinusoidal landscape
  undergoing Brownian motion.
  We increase the temperature relative
  to the amplitude of the landscape
  troughs until the particle enters a hopping regime.
  In  Fig.~\ref{fig:brownian}(a)
  the temperature is $T/A_p = 4.0$.
  The particle executes a 
  random walk centered at the potential minima $y/\lambda = 10$.
  We ran many simulations and never observed a hop to another minima
  within this simulation time.  
  In  Fig.~\ref{fig:brownian}(b)
  $T/A_p = 5.0$ where hops between
  potential minima are possible but not probable,
  a single hop occurs from
  $y/\lambda = 10$ to $y/\lambda = 12$ at
  $t \sim 40000 \tau$ and 
  $y/\lambda = 10$ to $y/\lambda = 8$ at
  $t \sim 280000 \tau$.
  In other simulations with identical parameters,
  we sometimes observed no hops or two hops between minima,
  as expected with random fluctuating systems.
  In  Fig.~\ref{fig:brownian}(c)
  $T/A_p = 6.0$ 
  we observe many hops.
  The random thermalized kicks are
  sufficiently large to make the particle perform
  what appears to be 
  a random walk of hops atop the substrate.
  %in addition to the small scale random walk executed
  %by all particles in this section.

@@

  In Fig.~\ref{fig:hops}
  we show the effects of lowering the frequency
  of applied driving force,
  holding the remaining parameters fixed 
  to 
  $F^{dc}=0.1$, $F^{ac}=0.05$, and $A_p = 0.1$.
  We observe no backward steps 
  ($n_b = 0$) 
  across a broad range of frequencies.
  The number of forward steps 
  $n_f$ increases as frequency decreases.
  Low frequencies
  result in sustained positive or negative motion of a particle,
  where in Fig.~\ref{fig:hops}(e)
  the particle reaches the top edge of the system
  and wraps back to $y=0$.
  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{parameters_fig5}.pdf}
      \caption{
        Motion of a particle with the same values of $F^{dc} = 0.1$ and $F^{ac} = 0.05$ as Fig.~\ref{fig:0} and decreasing frequency as marked.
        In (e) the particle wraps the periodic boundary conditions.
      }
      \label{fig:hops}
    \end{figure}
  \end{center}
  %In Fig.~\ref{fig:hops}

  In Fig.~\ref{fig:hops_back}
  we fix $f=0.01$, $F^{dc}=0.1$, and and $A_p = 0.1$.
  We show the results for increasing $F^{ac} = 0.2, 0.3, 0.4$.
  %of the system for our original parameters.
  Here $n_b$ increases from $n_b = 0$ in (a) to
  $n_b = 2$ in (b) to $n_b = 4$ in (c).  
  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{parameters_fig6}.pdf}
      \caption{
        Motion of a particle with the same values of $F^{dc}$ and frequency as Fig.~\ref{fig:0} and increasing $F^{ac}$.
        (a) The particle moves forward six minima with no steps backward.
        (b) The particle moves forward eight minima with two steps backward.
        (c) The particle moves forward nine minima with four steps backward.
      }
      \label{fig:hops_back}
    \end{figure}
  \end{center}
  %In Fig.~\ref{fig:hops}

    \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{fig7_sweep_FDC_vs_vx}.pdf}
      \caption{
        Mode-locked steps in $\langle v_y \rangle$ vs. $F^{dc}$ of a particle with frequency $f=0.01$ and $F^{ac}=0.4$.  At low values of $F^{dc}$ the particle may move backwards, distorting the steps.
      }
      \label{fig:shapiro}
    \end{figure}
  \end{center}
  %In Fig.~\ref{fig:hops}
%\item Frenkel-Kontorova and competing length scales for low temperature systems where thermal fluctuations are negligible
%  \item The Fokker-Planck Equation
%  \item Aubrey-Kontorova + commensurability
%  \item nanotribology
 %   kink motion
 %   Vanossi et al J.Phys.: Condens. Matter 19 (2007)
  %\item

@@

\section{Conclusion}
\label{sec:conclusion}	% You can label sections for reference

%Fundamental models
%of synchronization 
%can %include many coupled oscillators
%or
%focus on
%We have driven 
A single particle driven across a periodic potential landscape 
%Single particle studies are useful
synchronizes its motion %to study synchronization dynamics
%that arise
to environmental and external forces,
a phenomena known as mode-locking.  
%due to interactions between particles.
Our simulations reproduce experiments presented in 
Juniper {\it et al.} \cite{Juniper2015} %, Juniper2018}
of 
mode locking in
%experiments and simulations of 
driven colloids on a
periodic optical landscape.
Colloids are 
relatively easy to 
manipulate and image in experiments,
making ideal proxies 
for systems %relatively
such as cold atoms or electron gases \cite{Grier2003}.
%which are 
%hard to access and visualize 
%Collections of colloids can
%be used to study the properties of solids and liquids
%or more exotic systems 
%Oscillators ordered into chains or lattices.
%has many important
%technological applications
Dynamical mode-locking %, the primary synchronization
%effect explored in this paper, 
is %often
observed
in quantum electronic
devices %, such as Josephson junctions \cite{Josephson1962,Josephson1965}, 
%A single junction contains 
%two superconductoring layers which sandwich an insulating layer.
%When subject to an external voltage,
%Cooper pairs in the superconducting materials
%tunnel through the insulating layer.
%Phase-locking is observed in these devices
as 
stepped regions in current-voltage (I-V) relationship,
where voltage is the analog of external driving force
and current is that of particle velocity.
Known as Shapiro steps, % \cite{},
these mode-locked or phase-locked currents  
have been observed due to applied ac voltages in 
single Josephson junctions \cite{Shapiro1963, Golubov2004} and
coupled arrays of junctions \cite{Benz1990}.
Shapiro steps vary in width depending on the strength of the
applied ac forces,
and are observed in a variety of ac and dc driven systems
displaying
%are hallmarks of
non-Ohmic behavior in voltage-current curves,
including
charge waves, spin density waves
and superconducting vortices in landscapes 
engineered with periodic patterns of pinning sites.
%Thus the study of
Mode-locking is a useful probe 
of complex quantum mechanical systems
since the motions of individual particles can only be inferred
from other measurements.
Our results can be relevant 
to synchronization effects
in a broad range of experiments systems
including optically confined colloids,
superconductors with periodic pinning arrays, 
and the charge and spin of atomic systems.

@@

      \bibitem{Pertsinidis2001} A. Pertsinidis, and X. Ling,  Equilibrium Configurations and Energetics of Point Defects in Two-Dimensional Colloidal Crystals. {\it Phys Rev Lett}, {\bf 87}, 098303 (2001). %https://doi.org/10.1103/PhysRevLett.87.098303

@@

      %quote: Phase engineering techniques are used to control the dynamics of long-bosonic Josephson-junction arrays built by linearly coupling Bose-Einstein condensates.

    \bibitem{Zhang2020} Dengling Zhang, Haibo Qiu, and Antonio Muñoz Mateo, Unlocked-relative-phase states in arrays of Bose-Einstein condensates, Phys. Rev. A {\bf 101}, 063623 (2020).
